### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

  Authors response: We acknowledge that in the paper, 
  we only deal explicitly with SNARE proteins. Although 
  it is not required for an understanding of the work, 
  we feel a glimpse of the kinds of processes involved 
  in vesicle traffic, and its molecular machinery might 
  help the reader appreciate why we have built our model 
  in this particular way.

  > That the steady-state condition corresponds to the 
    biological meaning of homeostasis is repeated. This 
    only needs to be mentioned once.

  Authors response: We now state the equivalence of our 
  steady state condition and homeostasis of compartments
  only in section 2.3.2.

  > There is overlap in the 3rd and 6th paragraphs of 
    the 'Related Work' section, which refer to the use 
    of SAT/SMT in GRNs.
  Authors response: The use of SAT/SMT in GRN is presented
  in two different context (non-overlapping references). 
  The third paragrah points to general use of SAT/SMT 
  solvers in GRN, whereas 6th paragraph refers to a specific
  use (synthesis). We have updated the text to improve this
  distinction.

### 2019-09-09 papers/journal/related.tex
related work

There has been some work in applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}. The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis. The paper~\cite{cardelli2017syntax} in addition to using SMT over ODE, uses a template-guided approach. In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. To our best knowledge, this is the first application of synthesis in VTS.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

There has been some work in applying synthesis technique in biology. %especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. 
A recent work by \cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
%
In \cite{shavit2016automated} synthesis of switching GRN (with changing topology) is performed.
%
The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques whereas \cite{shavit2016automated} uses SMT to perform synthesis. 
%
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
%
%
The work
%The paper \cite{cardelli2017syntax} in addition to using SMT over  ODE, 
use a template-guided approach in addition to using SMT over ODE. In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. 
%
To our best knowledge, this is the first application of synthesis in VTS.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
